Computable Poincar\'e--Friedrichs constants\\ for the $L^{p}$ de Rham complex over domains\\ with shellable triangulations

### 2024-09-08 main.tex
major update

\begin{remark}
    % The main feature in proving these results is that the best constant in the Poincar\'e inequality is already the constant in the $1$-dimensional case. 
    Any estimate for the Poincar\'e--Friedrichs constant implies an estimate for the Poincar\'e constant, via~\eqref{math:p_vs_pf}
    Let us compare the estimate $C_{{\rm P},{\rm CW},p}$ for the Poincar\'e constant
    with the estimate obtained from the Poincar\'e--Friedrichs constant $C_{{\rm PF},{\rm EFNT},p}$. 
    In the case $2 \leq p$, 
    \begin{align*}
        2^{1-\frac 2 p}
        C_{{\rm PF},{\rm EFNT},p}
        =
        \frac{ 2^{1-\frac 2 p} }{2}
        \frac{ \sin(\pi/p) }{ \pi/p }
        \frac{ 1 }{ \sqrt[p]{p-1} }
        \leq 
        4^{-\frac 1 p}
        \leq
        C_{{\rm P},{\rm CW},p} 
        .
    \end{align*}
    In the case $2 \geq p$, 
    \begin{align*}
        2^{\frac 2 p - 1}
        C_{{\rm PF},{\rm EFNT},p}
        =
        \frac{ 2^{\frac 2 p - 1} }{2}
        \frac{ \sin(\pi/p) }{ \pi/p }
        \frac{ 1 }{ \sqrt[p]{p-1} }
        \leq
        \frac{ 2^{\frac 2 p-1} }{2}
        &
        =
        2^{\frac 2 p - 2}
        \\&
        =
        4^{\frac 1 p - 1}
        \leq
        C_{{\rm P},{\rm CW},p} 
%         % 
%         .
%         4^{\frac 1 p}
%         \frac{ p \sin(\pi/p) }{ 2\pi \sqrt[p]{p-1} \cdot 2 }
%         =
%         4^{\frac 1 p}
%         \frac{ p \sin(\pi/p) }{ 4\pi \sqrt[p]{p-1} }
%         \leq 
%         \frac 1 2
        .
    \end{align*}
    It follows that \eqref{math:esposito:poincare} is generally tighter estimate than \eqref{math:chuawheeden} for $1 < p < \infty$.
    % DONE: what exactly is the limit as p -> 1 ? It converges to 1.
    % DONT: insert the original inequality by chua and Wheeden
    % DONE: chua wheeden upper bound is not optimal!
    % DONE: Theorem 1.2 in Chua Wheeden 
% DONT: Keep ?
%     In the limit as $p$ goes to $1$, the factor $C_{{\rm PF},{\rm EFNT},p}$ converges to $1/2$,
%     which is the optimal Poincar\'e--Friedrichs constant and also the optimal factor in the Poincar\'e inequality \eqref{math:acostaduran}
%     \begin{align*}
%         \| u - u_{\Omega} \|_{L^{1}(\Omega)}
%         \leq 
%         \frac{1}{2}
%         \diam(\Omega)
%         \| \nabla u \|_{L^{1}(\Omega)}
%         ,
%         \quad
%         \forall 
%         u \in W^{1,1}(\Omega)
%         .
%     \end{align*}
%     In the limit as $p$ goes to infinity, the factor $C_{{\rm PF},{\rm EFNT},p}$ converges to $1/2$, 
%     which implies the Poincar\'e inequality 
%     \begin{align*}
%         \| u - u_{\Omega} \|_{L^{\infty}(\Omega)}
%         \leq 
%         \diam(\Omega)
%         \| \nabla u \|_{L^{\infty}(\Omega)}
%         ,
%         \quad
%         \forall 
%         u \in W^{1,\infty}(\Omega)
%         %
%     \end{align*}
%     because the $L^{\infty}$-norm is the limit of the $L^{p}$-norm. % DONT: cite 
%     % DONT: review this entire result 
\end{remark}

@@

        \item 
        We let $z'_{S}$ be the midpoint of $S'$. 
        We first define a new triangulation $\calS$ by the barycentric refinement of the complementary $S'$. 
        All $n$-simplices in $\calS$ contain $S$ and $z'_{S}$.

@@

        \item 
        We introduce a new mapping $\Theta : |\calR| \rightarrow |\calR^c|$.
        Let $K \in \calR$ be an $n$-simplex and $K' \in \calR^{c}$ be constructed from $K$.
        We let $A_{K} : \Delta^{n} \rightarrow K$ and $A_{K'} : \Delta^{n} \rightarrow K'$
        be affine reference transformations
        that agree on the vertices common to $K$ and $K'$.
        We then define 
        \begin{align*}
            \Theta_{|K} := A_{K'} \circ A_{K}^{-1}.
        \end{align*}
        Notice that $A_{K'}$ and $A_{K}$ have the same singular values. Thus
        \begin{align*}
            \| \Jacobian \Theta_{|K}      \| &\leq \| A_{K'} \| \cdot \| A_{K}^{-1} \| \leq \kappa(A_{K}),
            \\
            \| \Jacobian \Theta_{|K}^{-1} \| &\leq \| A_{K'}^{-1} \| \cdot \| A_{K} \| \leq \kappa(A_{K}).
        \end{align*}
        \color{red}
        By construction, 
        \begin{align*}
            \det( \Jacobian \Theta_{|K} )
            = 
            \det( \Jacobian^{-1} \Theta_{|K} )
            =
            1
            .
        \end{align*}
        \color{black}

@@

In what follows, use the abbreviation
\begin{align*}
    C_{{\rm PF},\Gamma,k,p}(\calT) 
    :=
    \max\limits_{ \substack{ T \in \calT \; \dim(T)=n \\ 0 \leq l \leq n } }
    C_{{\rm PF},\Gamma,l,k,p}(T)   
\end{align*}
whenever $\calT$ is an $n$-dimensional triangulation.

>>>>

\begin{remark}
    % The main feature in proving these results is that the best constant in the Poincar\'e inequality is already the constant in the $1$-dimensional case. 
    Any estimate for the Poincar\'e--Friedrichs constant implies an estimate for the Poincar\'e constant, via~\eqref{math:p_vs_pf}
    Let us compare the estimate $C_{{\rm P},{\rm CW},p}$ for the Poincar\'e constant
    with the estimate obtained from the Poincar\'e--Friedrichs constant $C_{{\rm PF},{\rm EFNT},p}$. 
    In the case $2 \leq p$, 
    \begin{align*}
        2^{1-\frac 2 p}
        C_{{\rm PF},{\rm EFNT},p}
        =
        \frac{ 2^{1-\frac 2 p} }{2}
        \frac{ \sin(\pi/p) }{ \pi/p }
        \frac{ 1 }{ \sqrt[p]{p-1} }
        \leq 
        4^{-\frac 1 p}
        \leq
        C_{{\rm P},{\rm CW},p} 
        .
    \end{align*}
    In the case $2 \geq p$, 
    \begin{align*}
        2^{\frac 2 p - 1}
        C_{{\rm PF},{\rm EFNT},p}
        =
        \frac{ 2^{\frac 2 p - 1} }{2}
        \frac{ \sin(\pi/p) }{ \pi/p }
        \frac{ 1 }{ \sqrt[p]{p-1} }
        \leq
        \frac{ 2^{\frac 2 p-1} }{2}
        &
        =
        2^{\frac 2 p - 2}
        \\&
        =
        4^{\frac 1 p - 1}
        \leq
        C_{{\rm P},{\rm CW},p} 
%         % 
%         .
%         4^{\frac 1 p}
%         \frac{ p \sin(\pi/p) }{ 2\pi \sqrt[p]{p-1} \cdot 2 }
%         =
%         4^{\frac 1 p}
%         \frac{ p \sin(\pi/p) }{ 4\pi \sqrt[p]{p-1} }
%         \leq 
%         \frac{1}{2}
        .
    \end{align*}
    It follows that \eqref{math:esposito:poincare} is generally tighter estimate than \eqref{math:chuawheeden} for $1 < p < \infty$.
    % DONE: what exactly is the limit as p -> 1 ? It converges to 1.
    % DONT: insert the original inequality by chua and Wheeden
    % DONE: chua wheeden upper bound is not optimal!
    % DONE: Theorem 1.2 in Chua Wheeden 
% DONT: Keep ?
%     In the limit as $p$ goes to $1$, the factor $C_{{\rm PF},{\rm EFNT},p}$ converges to $1/2$,
%     which is the optimal Poincar\'e--Friedrichs constant and also the optimal factor in the Poincar\'e inequality \eqref{math:acostaduran}
%     \begin{align*}
%         \| u - u_{\Omega} \|_{L^{1}(\Omega)}
%         \leq 
%         \frac{1}{2}
%         \diam(\Omega)
%         \| \nabla u \|_{L^{1}(\Omega)}
%         ,
%         \quad
%         \forall 
%         u \in W^{1,1}(\Omega)
%         .
%     \end{align*}
%     In the limit as $p$ goes to infinity, the factor $C_{{\rm PF},{\rm EFNT},p}$ converges to $1/2$, 
%     which implies the Poincar\'e inequality 
%     \begin{align*}
%         \| u - u_{\Omega} \|_{L^{\infty}(\Omega)}
%         \leq 
%         \diam(\Omega)
%         \| \nabla u \|_{L^{\infty}(\Omega)}
%         ,
%         \quad
%         \forall 
%         u \in W^{1,\infty}(\Omega)
%         %
%     \end{align*}
%     because the $L^{\infty}$-norm is the limit of the $L^{p}$-norm. % DONT: cite 
%     % DONT: review this entire result 
\end{remark}

@@

        \item 
        We let $z'_{S}$ be the midpoint of $S'$. 
        We first define a new triangulation $\calS$ by the barycentric refinement of the complementary simplex $S'$. 
        All $n$-simplices in $\calS$ contain $S$ and $z'_{S}$.

@@

        We introduce a new mapping $\Theta : |\calR| \rightarrow |\calR^c|$.
        Let $K \in \calR$ be an $n$-simplex and $K' \in \calR^{c}$ be constructed from $K$.
        We let $A_{K} : \Delta^{n} \rightarrow K$ and $A_{K'} : \Delta^{n} \rightarrow K'$
        be affine reference transformations
        that agree on the vertices common to $K$ and $K'$.
        We then define 
            \Theta_{|K} := A_{K'} \circ A_{K}^{-1}.
        Notice that $A_{K'}$ and $A_{K}$ have the same singular values. Thus
            \| \Jacobian \Theta_{|K}      \| &\leq \| A_{K'} \| \cdot \| A_{K}^{-1} \| \leq \kappa(A_{K}),
            \| \Jacobian \Theta_{|K}^{-1} \| &\leq \| A_{K'}^{-1} \| \cdot \| A_{K} \| \leq \kappa(A_{K}).
        \color{blue}
        By construction, 
            |\det( \Jacobian      \Theta_{|K} )|
            |\det( \Jacobian^{-1} \Theta_{|K} )|
        We $h_z \in \bbR^{n}$ be the height vector of $z_{S'}$ inside the simplex $K$.
        Clearly,
            \Theta_{|K}(x) 
            2 \hat z_{S'} \frac{\langle \hat h_z, x \rangle}{\langle \hat h_z, \hat z_{S'} \rangle}
        Indeed, we check that the right-hand side equals $x$ whenever $x$ lies in the plane orthgonal to $\hat h_z$,
        and when $x = z_{S'}$, then 
            -z_{S'} 
            z_{S'}
            2 \hat z_{S'} \frac{\langle \hat h_z, z_{S'} \rangle}{\langle \hat h_z, \hat z_{S'} \rangle}
        If we orthogonally decompose $z_{S'} = h_z + b_z$, then 
            \Theta_{|K}( h_z ) 
            h_z
            2 z_{S'} \frac{\langle h_z, h_z \rangle}{\langle h_z, z_{S'} \rangle}
            h_z
            2 z_{S'}
            - h_{z}
            2 b_{z}
        Let $\beta$ be the angle between $z_{S'}$ and $h_{z}$. 
        Then $\| h_z \| = \cos(\beta) \|z_{S'}\|$ and $\| b_z \| = \sin(\beta) \|z_{S'}\|$. 
        We study the singular values of the matrix 
            \begin{pmatrix}
            -1                 & 0
            -2 \|b_z\|/\|h_z\| & 1
            \end{pmatrix}
            \begin{pmatrix}
            -1             & 0
            -2 \tan(\beta) & 1
            \end{pmatrix}
            \begin{pmatrix}
            0             & \tan(\beta)
            -\tan(\beta) & 0
            \end{pmatrix}
            \begin{pmatrix}
            -1           & -\tan(\beta)
            \tan(\beta) & 1
            \end{pmatrix}
        It follows that $\det(\Theta_{|K}) = 1$. 
        Its singular values satisfy 
            ( \sigma_{\max} + \sigma_{\min} )/2
            \tan(\beta)
            \qquad 
            ( \sigma_{\max} - \sigma_{\min} )/2
            \sqrt{ 1 + \tan^{2}(\beta) }
        which means that 
            \sigma_{\max} = \sqrt{ 1 + \tan^{2}(\beta) } + \tan(\beta)
            \qquad 
            \sigma_{\min} = \sqrt{ 1 + \tan^{2}(\beta) } - \tan(\beta)
        Let $\beta$ be the angle between $z_{S'}$ and $h_{z}$. 
        By the definition of the cosine, $\cos(\beta) \leq \| h_{z} \| / \| z_{S'} \|$. 
        Let $F_{z} \subseteq K$ be the face opposite to $z_{S'}$,
        which is also a face of $T$. Then $(n-k-1) h_{z}$ is the height vector of $F_{z}$ in $T$. 
        Thus 
            \frac{ \| h_{z} \| }{ \| z_{S'} \| }
            \frac{ (n-k-1)^{-1} \| (n-k-1) h_{z} \| }{ \| z_{S'} \| }
            \frac{ (n-k-1)^{-1} n \vol(T) }{ \| z_{S'} \| \vol(F_{z}) }
            \frac{n}{ n-k-1 }
            \frac{ \vol(T) }{ \diam(T)^{n} }
%             \\
%             \frac{ n \vol(K) }{ \| z_{S'} \| \vol(F_{z}) }
%             \frac{ \vol(T) }{ \| z_{S'} \| \vol(F_{z}) }
%             \frac{ \vol(T) }{ \diam(T)^{n} }

What are the singular values of a $2x2$ (lower) unit triangular matrix? Suppose we have the matrix
Suppose we have the matrix 
\begin{align*}
    \begin{pmatrix}
    1 & 0
    \\ 
    b & 1
    \end{pmatrix}
\end{align*}
Following up a generic formula found here, 
https://math.stackexchange.com/a/861774/3557
I decompose 
\begin{align*}
    \begin{pmatrix}
    1 & 0
    \\ 
    b & 1
    \end{pmatrix}
    =
    \frac 1 2 
    \begin{pmatrix}
    2 & -b
    \\ 
    b & 2
    \end{pmatrix}
    +
    \frac 1 2 
    \begin{pmatrix}
    0 & b
    \\ 
    b & 0
    \end{pmatrix}
\end{align*}
The singular values $w_1$ and $w_2$ are implicitly given by 
\begin{align*}
    \frac{ w_1 + w_2 }{2} = \frac 1 2 \sqrt{ 4 + b^2 }
    \\
    \frac{ w_1 - w_2 }{2} = \frac 1 2 |b|
\end{align*}
If we assume that the first value is at least the second value, 
then adding and subtracting these equations leads to 
\begin{align*}
    w_1 = \frac 1 2 \sqrt{ 4 + b^2 } + \frac 1 2 |b|
    \\
    w_2 = \frac 1 2 \sqrt{ 4 + b^2 } - \frac 1 2 |b|
\end{align*}
I would like to know whether that reasoning is correct

foo
\begin{align*}
    \lambda^2 = \frac{1}{2} \left( a + c \pm \sqrt{ a^2 - 2 a c + c^2 + 4b^2 } \right)
\end{align*}
\begin{align*}
    \lambda 
    &= 
    \frac{1}{\sqrt 2} \sqrt{ (1+t^2) + 1 \pm \sqrt{ (1+t^2)^2 - 2 (1+t^2)   +   1 + 4t^2 } } 
    \\
    &= 
    \frac{1}{\sqrt 2} \sqrt{ t^2 + 2 \pm \sqrt{ 1 + 2t^2 + t^4 - 2 - 2 t^2 + 1 + 4t^2 } } 
    \\
    &= 
    \frac{1}{\sqrt 2} \sqrt{ t^2 + 2 \pm \sqrt{          + t^4                 + 4t^2 } } 
    \\
    &= 
    \frac{1}{\sqrt 2} \sqrt{ t^2 + 2 \pm t \sqrt{ t^2 + 4 } } 
    .
\end{align*}
\begin{align*}
    \lambda = \frac{1}{\sqrt 2} \sqrt{ t^2 + 2 \pm t \sqrt{ t^2 + 4 } } 
\end{align*}
\begin{align*}
    \left( t^2 + 2 + t \sqrt{ t^2 + 4 } \right)
    \left( t^2 + 2 - t \sqrt{ t^2 + 4 } \right)
    =
    t^{4} + 4 t^{2} + 4
    -
    t^{2} ( t^{2} + 4 )
    =
    4
\end{align*}
\begin{align*}
    \frac{1}{\sqrt 2} \sqrt{ t^2 + 2 \pm t \sqrt{ t^2 + 4 } } 
    &=
    \sqrt{1+a^2/4} \pm a/2
    \\
    \frac 1 2 \left( t^2 + 2 \pm t \sqrt{ t^2 + 4 } \right)
    &=
    1+a^2/4
    \pm
    a \sqrt{1+a^2/4}
    + 
    a^2/4
    \\&=
    1
    +
    2a^2/4
    \pm
    a \sqrt{1+a^2/4}
    \\
    1 + \frac{t^2}{2} \pm t \sqrt{ \frac{t^2}{4} + 1 } 
    &=
    1
    +
    a^2/2
    \pm
    a \sqrt{1+a^2/4}
    .
\end{align*}

        \item 
        We prove another auxiliary result.
        Let $x, h_1, h_2 \in \bbR^{n}$ be non-zero. 
        Define 
        \begin{align*}
            F(x) 
            = 
            \frac{ \| h_2 \|^{2} }{ \langle h_2, x \rangle }
            \frac{ \langle h_1, x \rangle }{ \| h_1 \|^{2} }
            x
            .
        \end{align*}
        This is defined away from the hyperplane orthogonal to $h_2$.
        This is a radial mapping that maps each point on the hyperplane defined by the normal vector $h_1$
        onto the colinear point that lies on the hyperplane defined by the normal vector $h_2$. Indeed, 
        if $x \in \bbR^{n}$ with $\langle h_1, x \rangle = \| h_1 \|^{2}$, then $\langle F(x), h_2 \rangle = \| h_2 \|^{2}$.

        We identify the Lipschitz properties of this mapping by computing its Jacobian. 
        We write $\alpha_1, \alpha_2 \geq 0$ for the two angles between $h_1$ and $h_2$, respectively, and the vector $x$.
        In what follows, $y \in \bbR^{n}$.
        \begin{align*}
            \Jacobian F(x) \cdot y
            &=
            \frac{ \langle h_2, h_2 \rangle }{ \|h_2\| \|x\| \cos(\alpha_2) }
            \left( y - \frac{ \langle h_2, y \rangle }{ \langle h_2, x \rangle } x \right)
            \frac{ \langle x, h_1 \rangle }{ \langle h_1, h_1 \rangle }
            +
            x
            \otimes 
            \frac{ \| h_2 \|^{2} }{ \langle h_2, x \rangle }
            \frac{ h_1^{t} y }{ \| h_1 \|^{2} }
            \\&=
            \frac{ \langle \hat h_2, h_2 \rangle }{ \cos(\alpha_2) }
            \left( y - \frac{ \langle \hat h_2, y \rangle }{ \langle \hat h_2, \hat x \rangle } \hat x \right)
            \frac{ \langle \hat x, \hat h_1 \rangle }{ \langle h_1, \hat h_1 \rangle }
            +
            \hat x
            \otimes 
            \frac{ \| h_2 \| }{ \langle \hat h_2, \hat x \rangle }
            \frac{ \hat h_1^{t} y }{ \| h_1 \| }
            \\&=
            \frac{ \| h_2 \| }{ \cos(\alpha_2) }
            \left( y - \frac{ \langle \hat h_2, y \rangle }{ \cos(\alpha_2) } \hat x \right)
            \frac{ \cos(\alpha_1) }{ \| h_1 \| }
            +
            \hat x
            \otimes 
            \frac{ \| h_2 \| }{ \langle \hat h_2, \hat x \rangle }
            \frac{ \hat h_1^{t} y }{ \| h_1 \| }
            \\&=
            \frac{ \| h_2 \| }{ \| h_1 \| }
            \frac{ \cos(\alpha_1) }{ \cos(\alpha_2) }
            \left( 
                y 
                - 
                \frac{ \langle \hat h_2, y \rangle }{ \cos(\alpha_2) } \hat x 
                + 
                \frac{ \langle \hat h_1, y \rangle }{ \cos(\alpha_1) } \hat x 
            \right)
            .
        \end{align*}
        We define $a := \cos(\alpha_1)^{-1} \hat h_1 - \cos(\alpha_2)^{-1} \hat h_2$. 
        Notice that $a \perp \hat x$ by definition. The matrix $\Id + \hat x \otimes a^{t}$ is the identity over the orthogonal complement of the linear span of $a$ and $x$. Over that two-dimensional subspace, it can be represented by a triangular matrix.
        Its largest and the smallest singular values $\sigma_{max} \geq 1 \geq \sigma_{\min}$ are~\cite{blinn1996consider} 
        \begin{align*}
            \sigma_{\max} = \sqrt{ 1 + \frac{ \|a\|^{2} }{ 4 } } + \frac{ \|a\| }{2},
            \qquad 
            \sigma_{\min} = \sqrt{ 1 + \frac{ \|a\|^{2} }{ 4 } } - \frac{ \|a\| }{2}.     
        \end{align*}
        Notice that these are strictly monotonely increasing or decreasing, respectively, in $\|a\|$.
        We notice the obvious upper bound 
        \begin{align*}
            \|a\| 
            \leq 
            2 \max_{1 \leq i \leq 2} 
            \left( 
                \frac{ \hat h_i }{ \langle \hat x, \hat h_i \rangle } 
            \right)
            .
        \end{align*}

        \item 
        We introduce a bi-Lipschitz mapping 
        \begin{align*}
            \Psi : |\calR'| \rightarrow |\calK|
        \end{align*}
        in the following manner. Let ${G} \in \calR'$ be an $n$-dimensional simplex and let $x \in {G}$ be non-zero. There exists a simplex $K \in \calK$ that intersects the ray $\bbR_0^+ \cdot x$. We let $h_{{G}}$ and $h_{K}$ be the normals of the origin within ${G}$ and $K$, respectively. They define respective hyperplanes $H_{G}$ and $H_{K}$,
        and we write $F_{G} = G \cap H_{G}$ and $F_{K} = K \cap H_{K}$. 
        We notice that $x$ has a sharp angle to both $h_{{G}}$ and $h_{K}$. 
        We define 
        \begin{align*}
            \Psi(x) 
            = 
            \frac{ \| h_K \|^{2} }{ \langle h_K, x \rangle }
            \frac{ \langle h_{{G}}, x \rangle }{ \| h_{{G}} \|^{2} }
            x
            .
        \end{align*}
        One easily verifies that this defines a continuous mapping $\Psi$. 
        By the same line of thought, we see that it is invertible with inverse satisfying 
        \begin{align*}
            \Psi^{-1}(z) 
            = 
            \frac{ \| h_{{G}} \|^{2} }{ \langle h_{{G}}, z \rangle }
            \frac{ \langle h_K, z \rangle }{ \| h_K \|^{2} }
            z,
            \qquad 
            z = \Psi(x)
            .
        \end{align*}
        Our previous observations enable estimates for the Jacobians. 
        We have the operator norm and determinant formulas 
        \begin{gather*}
            \| \Jacobian\Psi(x) \|
            = 
            \frac{ \| h_K \| }{ \| h_{{G}} \| }
            \frac{ \cos(\alpha_{{G}}) }{ \cos(\alpha_K) }
            \left( 
                \sqrt{ 1 + \frac{ \|a\|^{2} }{ 4 } } + \frac{ \|a\| }{2}
            \right)
            \\
            \| \Jacobian\Psi(z)^{-1} \|
            = 
            \frac{ \| h_{{G}} \| }{ \| h_K \| }
            \frac{ \cos(\alpha_K) }{ \cos(\alpha_{{G}}) }
            \left( 
                \sqrt{ 1 + \frac{ \|a\|^{2} }{ 4 } } - \frac{ \|a\| }{2}
            \right)^{-1},
            \\
            \det\Jacobian\Psi(x)
            =
            \left( 
            \frac{ \| h_K \| }{ \| h_{{G}} \| }
            \frac{ \cos(\alpha_{{G}}) }{ \cos(\alpha_K) }
            \right)^{n},
            \qquad
            \det\Jacobian\Psi^{-1}(x)
            =
            \left( 
            \frac{ \| h_{{G}} \| }{ \| h_{K} \| }
            \frac{ \cos(\alpha_{K}) }{ \cos(\alpha_{{G}}) }
            \right)^{n}
        \end{gather*}
        where $\alpha_K$ and $\alpha_{{G}}$ are the angles of $x$ with the vectors $h_{{G}}$ and $h_{K}$, respectively,
        and where $a := \cos(\alpha_{{G}})^{-1} \hat h_{{G}} - \cos(\alpha_K)^{-1} \hat h_K$.

        We let $x_{G} \in F_{G}$ and $x_{K} \in F_{K}$ be the intersection points of the ray $\bbR \cdot x$ with the respective faces.
        By the definition of the cosine, 
        \begin{align*}
            \frac{ \| h_K \| }{ \| h_{{G}} \| }
            \frac{ \cos(\alpha_{{G}}) }{ \cos(\alpha_K) }
            \leq 
            \frac{ \| x_K \| }{ \| h_{{G}} \| }
            \leq 
            \frac{ \diam(K) }{ \| h_{{G}} \| }
            ,
            \qquad 
            \frac{ \| h_{{G}} \| }{ \| h_K \| }
            \frac{ \cos(\alpha_K) }{ \cos(\alpha_{{G}}) }
            \leq 
            \frac{ \| x_{G} \| }{ \| h_{K} \| }
            \leq 
            \frac{ \diam(G) }{ \| h_{K} \| }
            .
        \end{align*}
%         \begin{align*}
%             \frac{ \| h_K \| }{ \| h_{{G}} \| }
%             \frac{ \cos(\alpha_{{G}}) }{ \cos(\alpha_K) }
%             \leq 
%             \frac{ \| x_K \| }{ \| x_{{G}} \| }
%             .
%         \end{align*}

        The diameters of the simplices in $\calK$ are already bounded by the maximum diameter in $\patch_{\calT}(S)$.
        The height $h_{K}$ is obtained from a height vector of a vertex in $\patch_{\calT}(S)$ by scaling with the factor $(k+1)^{-1}$.
        Every height of the origin in some simplex of $\calR'$ is obtained from a height vector of the origin in some simplex in $\calS'$
        by scaling with $(k+1)^{-1}$. Each of the latter height vectors has length bounded from below by the height of some vertex in $S$ within a simplex of $\calS$, multiplied by $\kappa(A)^{-2}$. The height of any vertex of $S$ in some simplex of $\calS$ is the same as the height $h_T$ of that vertex in the original simplex $T$. 
        In oder to estimate $\|x_{G}\|$, recall that $x = \lambda (-z_{S'}) + (1-\lambda) z_{x}$ for some $\lambda \in [0,1]$ and $z_{x} \in G$
        being in the face of $G$ that is opposite to $z_{x}$. The preimage of $x$ under $\Theta_{{G}}$ is $\lambda z_{S'} + (1-\lambda) z_{x}$. 
        It follows that $\|x_{G}\| \leq \diam(T)$.

        We know that whenever $T$ is a simplex with some face $F$ and $h_F$ is corresponding height vector, then 
        Recall that 
        \begin{align*}
            \frac{ \|h_{F}\|}{\diam(T)}
            = 
            \frac{ n \vol(T) }{ \vol(F) \diam(T) }
            \geq 
            \frac{ n \vol(T) }{ \diam(T)^{n} }
            \geq 
            (n-1)! \cdot \frac{ \diam(T)^{n} }{ n! \vol(T) }
            .
        \end{align*}
        We conclude that 
        \begin{gather*}
            \frac{ \diam(K) }{ \| h_{{G}} \| }
            \leq 
            (k+1)\kappa(A)^{2}
            \frac{ \diam(K) }{ \| h_{T} \| }
            \leq 
            (k+1)\kappa(A)^{2}
            \theta(\calT)
            \frac{ \diam(T) }{ \| h_{T} \| }
            \leq 
            (k+1)\kappa(A)^{2}
            (n-1)! \cdot \frac{ \diam(T)^{n} }{ n! \vol(T) }
            ,
            \\
            \frac{ \| x_{G} \| }{ \| h_{K} \| }
            \leq 
            (k+1)
            \frac{ \diam(T) }{ \| h_{K} \| }
            \leq 
            (k+1)
            \theta(\calT)
            \frac{ \diam(K) }{ \| h_{K} \| }
            \leq 
            (k+1)
            \theta(\calT)
            \sup_{ K \in \patch_{\calT}(S) }
            (n-1)! \cdot \frac{ \diam(K)^{n} }{ n! \vol(K) }
            .
        \end{gather*}
        \begin{gather*}
            \frac{ \diam(K) }{ \| h_{{K}} \| }
            \leq 
            (k+1)
            \sup_{ K \in \patch_{\calT}(S) }
            (n-1)! \cdot \frac{ \diam(K)^{n} }{ n! \vol(K) }
            ,
            \\
            \frac{ \| x_{G} \| }{ \| h_{G} \| }
            \leq 
            (k+1)\kappa(A)^{2}
            (n-1)! \cdot \frac{ \diam(T)^{n} }{ n! \vol(T) }
            .
        \end{gather*}

        %         To simplify that expression, we make another observation regarding the height vectors. 
        %         when $T$ is an $n$-dimensional simplex with a $k$-dimensional subsimplex $S \subseteq T$,
        %         and $h > 0$ is the height of some vertex $v \in S$ opposite to a face $F$,
        %         then the barycenter $z_S$ of $S$ has distance $h/(k+1)$ from the face $F$. 
        %         From this obversation we infer that the height vectors at the origin of the simplices in $\calR'$ and $\calK$
        %         are obtained by rescaling the height vectors in $\calS'$ and $\patch_{\calT}(S)$
        %         with the factor $(k+1)^{-1}$.

        The vector $a$ is the difference between $\hat h_{G}$ and $\hat h_{K}$ after both are rescaled such that they lie on the affine hyperplane with normal vector $\hat x$. That difference has length at most $\tan(\alpha_{G}) + \tan(\alpha_{K})$.
        We calculate 
        \begin{align*}
            \|a\|
            = 
            \left\|
            \frac{\|x_{G}\|}{\|h_{G}\|} \hat h_{{G}} 
            - 
            \frac{\|x_{K}\|}{\|h_{K}\|} \hat h_K
            \right\|
            &
            \leq 
            \frac{\|x_{G}\|}{\|h_{G}\|} 
            + 
            \frac{\|x_{K}\|}{\|h_{K}\|} 
            \\&
            \leq 
            (k+1) 
            (n-1)! \cdot 
            \left( 1 + \kappa(A)^{2} \right)
            \sup_{ K \in \patch_{\calT}(S) }
            \frac{ \diam(K)^{n} }{ n! \vol(K) }
            .
        \end{align*}
        \todo{bound $\kappa(A)$ right away...}

        \item 
        We define a mapping $ \Xi : T \rightarrow U = \overline{\patch_{\calT}(S) \setminus T}$ by setting 
        \begin{align*}
            \Xi := \Psi \circ \Theta.
        \end{align*}
        It preserves the interface from $T$ onto $U$. We briefly recapitulate why it is bi-Lipschitz.

        We show that every function that is piecewise Lipschitz with respect to the triangulation $\calK$ must be Lipschitz over all of $|\calK|$. 
        We use a technique similar to Lemma~\ref{lemma:stars_are_shellable}. 
        After application of a piecewise linear Lipschitz mapping, 
        we can assume that $|\calK|$ is convex without loss of generality. 
        Any function piecewise Lipschitz with respect to $\calK$ must be Lipschitz over $|\calK|$. 
        By an application of Rademacher's theorem, we conclude that $\calK$ is bi-Lipchitz.

        We recall the upper bound $\sqrt{1+\theta^2} \leq 1 + \theta$ for any $\theta \geq 0$.

        \begin{align*}
            |\det(\Xi)|
            \leq 
            (k+1)^{n}
            (n-1)!^{n}
            \theta(\calT)^{n}
            \kappa(A)^{2n}
            \mu(\calT)
            ,
            \qquad 
            |\det(\Xi^{-1})|
            \leq 
            (k+1)^{n}
            (n-1)!^{n}
            \theta(\calT)^{n}
            \mu(\calT)
            .
        \end{align*}

        \color{black}

        \item 
        We introduce a bi-Lipschitz mapping 
        \begin{align*}
            \Psi : |\calR'| \rightarrow |\calK|
        \end{align*}
        in the following manner. Let ${G} \in \calR'$ be an $n$-dimensional simplex and let $x \in {G}$ be non-zero. There

@@

Whenever $\calT$ is an $n$-dimensional triangulation, we use the abbreviation
\begin{align*}
    C_{{\rm PF},\Gamma,k,p}(\calT) 
    :=
    \max\limits_{ \substack{ T \in \calT \; \dim(T)=n \\ 0 \leq l \leq n } }
    C_{{\rm PF},\Gamma,l,k,p}(T)   
\end{align*}

Suppose that an $n$-dimensional triangulation $\calT$ has a shelling $T_{0}, T_{1}, \dots, T_{M}$. 
For each $1 \leq m \leq M$, there exists a simplex $S_{m} \in \calT$ 
such that $T_{m}$ is the last $n$-simplex in the shelling that belongs to $T_{m} \in \patch_{\calT}(S_{m})$.
We then let $U_{m}$ be the closure $\patch_{\calT}(S_{m}) \setminus T_{m}$,
and we call it the complement of $T_{m}$ in the star $\patch_{\calT}(S_{m})$.
